Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
Make line wrapping nicer in a long list of citations.

This project is related to a variety of previous work, specifically in the realm
of security and verified proofs and programs.  We are following in the footsteps
of verified languages and compilers, which focus on writing programs and
language specs that are verified to have the properties the authors want by
providing the proofs of these properties on the
definitions~\cite{strecker2002formal,leinenbach2005towards,dave2003compiler,leroy2009formally,leroy2006formal,leroy2009formal,leroy2012compcert,chlipala2010verified,berghofer2004extracting}.
This has been a popular area, which is primarily focused on more mainstream
languages and compilers (such as C and Java).

>>>>

This project is related to a variety of previous work, specifically in the realm
of security and verified proofs and programs.  We are following in the footsteps
of verified languages and compilers, which focus on writing programs and
language specs that are verified to have the properties the authors want by
providing the proofs of these properties on the
definitions~\cite{strecker2002formal, leinenbach2005towards, dave2003compiler,
leroy2009formally, leroy2006formal, leroy2009formal, leroy2012compcert,
chlipala2010verified, berghofer2004extracting}.  This has been a popular area,
which is primarily focused on more mainstream languages and compilers (such as C
and Java).
